Synthesis of Rules for Network Intrusion Detectors

### 2019-10-25 paper/paper.tex
other updates

\begin{theorem}
  The minimization algorithm computes rules that capture only
  the positive traffic.
\end{theorem}
~
\begin{proof}
  Every rule created during the search captures the positive traffic
  as every rule contains a proper subset of the option from the
  original rule and all those options are satisfied by the positive
  traffic. By definition of function $\mathit{isfit}$, these rules
  also capture \emph{only} the positive traffic. If some negative
  traffic was captured, a rule would not be added to $\mathcal
  R'$.\qed
\end{proof}

@@

\vspace{1ex}
\noindent\textbf{Limitation.} It is worth noting that although
\tname{} is accurate for generating rules that discrimate positive and
negative traffic, the quality of these rules is limited by the quality
of the training data it uses. For the positive traffic, \tname{} only
requires one sample, but can benefit of several samples. For the
negative traffic, \tname{} can use public datasets available online.

\vspace{1ex}
\noindent\textbf{Implementation details.} \Fix{discuss function isFit}

@@

\subsection{Dataset of Benign Traffic}

@@

@@

\section{Threats to Validity}

@@

>>>>

\begin{theorem}
  The minimization algorithm computes rules that capture only
  the positive traffic.
\end{theorem}
\begin{proof}
  Every rule created during the search captures the positive traffic
  as every rule contains a proper subset of the option from the
  original rule and all those options are satisfied by the positive
  traffic. By definition of function $\mathit{isfit}$, these rules
  also capture \emph{only} the positive traffic. If some negative
  traffic was captured, a rule would not be added to $\mathcal
  R'$.\qed
\end{proof}

@@

\vspace{2ex}
\noindent\textbf{Limitation.} It is worth noting that although
\tname{} is accurate for generating rules that discrimate positive and
negative traffic, the quality of these rules is limited by the quality
of the training data it uses. For the positive traffic, \tname{} only
requires one sample, but can benefit of several samples. For the
negative traffic, \tname{} can use public datasets available online.

\vspace{2ex}
\noindent\textbf{Implementation details.} We implemented function
\emph{isFit} by 1)~updating Suricata to only use the informed rule,
2)~replaying the negative traffic (see
Section~\ref{sec:dataset-benign}), and 3)~reading the Suricata logs to
check if any benign message was captured by the rule. It is worth
noting that the benign traffic is stored in ``pcap'' files~\cite{pcap}
and Suricata can process those files very efficiently compared to
analyzing network messages directly.

@@

\subsection{Dataset of Benign Traffic}
\label{sec:dataset-benign}

@@

\Fix{}

@@

\subsection{Threats to Validity}

@@

\section{Conclusions}
